---
title: "Kaggle Competition Regression"
author: "Josha Thomas"
date: "5/31/2022"
output: html_document
---

```{r warning=FALSE, include=FALSE}

library(tidyverse)
library(tidymodels)
library(janitor)

```

```{r Load Data}

load("data_regression/initial_split_reg.rda")
load("model_info_regression/boost_tree_regression.rda")
load("model_info_regression/rand_forest_regression.rda")
read_csv("model_info_regression/boost_tree_reg_results.csv")

```

## EDA Results

Our overview of the shape of our numeric variables we can showed us that they are largely skewed to the right. Based on this information we decided to include a Yeo-Jonhson transformation in our recipe.

Our correlations shows us that most of our variables are not correlated. The variables that are correlated include (but are not limited to) the following hi_int_prncp_pd and out_prncp_inv, acc_now_delinq and num_tl_120dpd_2m, num_tl_30dpd and acc_now_delinq, acc_open_past_24mths and num_stats.

## Models Included

We found that boosted tree models preformed the best out of the models we tried. I tuned four parameters of the model including min_n, mtry, learning rate, and loss reduction.

## Model Results

```{r}

autoplot(object = boost_tree_tuned_reg, metric = "rmse")

autoplot(object = rand_forest_tuned_reg, metric = "rmse")

```

## Rankings

According to the kaggle my most successful model was my boosted tree regression model. It scored 857.20426 and is ranked 151. 

## Git Hub Repository

[Kaggle Competition Repository](https://github.com/joshathomas/Kaggle_Competition)
